---
title: "Lab 09"
author: "Conor Lacey"
date: '2023-03-17'
output: github_document
---

### Libraries

```{r Libraries}
library(tidyverse) 
library(broom)
library(openintro)
library(skimr)
```

### Exercise 1

```{r Score}
evals %>% ggplot(aes(x = score)) +
  geom_density(fill = "blue", alpha = 0.5)

summary(evals$score)
```

In general students rate courses pretty high. However, there it is skewed to the left. I would expect this as much, given that most students will do well in a class, getting a B or above and hence will give the professor a good rating. However, a few students will do exteremly poor in the class and hence blame some of their poor behavior on the professor. 

### Exercise 2

```{r score & bty_avg}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_point() 
```

In general, the relationship between score and beauty average appears to be random. 


```{r score & bty_avg cor}
cor(evals$score,evals$bty_avg)
```

Sure enough. The correlation is very small. 

### Exercise 3

```{r geom_jitter}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() 
```

Jitter here is adding a little bit of random variation to the location of each point. This helps in that the initial plot isn't doing this because the score variable is a discrete variable. What's misleading about the initial plot is that it assumes that there is no random variation when someone gives one particular score. Just because someone may give a score of 4 doesn't mean that their following the same criteria as someone else also giving that 4. Everyone gives that 4 for slightly different reasons. Jitter helps to communicate this. 

### Exercise 4

```{r m_bty}
m_bty <- lm(evals$score ~ evals$bty_avg)

summary(m_bty)
```

Linear model is: 

score = 3.88 + .067*bty_avg.

### Exercise 5

```{r evals plot with lm}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() + 
  stat_smooth(method = lm, se = FALSE, color = "orange")
```

### Exercise 6

Given the linear model, there is a positive relationship between score and beauty average such that as score increases so does beauty average. 

### Exercise 7

The intercept is 3.88 which means that with a score of 0 the mean average beauty rating is 3.88. I guess this would make sense. This is a relatively low score and I assume that those who do not do well in a class may hold animosity towards their professors such that they give them low beauty ratings. 

### Exercise 8 

The R^2 value is 0.035 meaning 3.5% of the variance in average beauty ratings can be explained by a professor's average evaluation score.
