---
title: "Lab 09"
author: "Conor Lacey"
date: '2023-03-17'
output: github_document
---

### Libraries

```{r Libraries}
library(tidyverse) 
library(broom)
library(openintro)
library(skimr)
```

### Exercise 1

```{r Score}
evals %>% ggplot(aes(x = score)) +
  geom_density(fill = "blue", alpha = 0.5)

summary(evals$score)
```

In general students rate courses pretty high. However, there it is skewed to the left. I would expect this as much, given that most students will do well in a class, getting a B or above and hence will give the professor a good rating. However, a few students will do exteremly poor in the class and hence blame some of their poor behavior on the professor. 

### Exercise 2

```{r score & bty_avg}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_point() 
```

In general, the relationship between score and beauty average appears to be random. 


```{r score & bty_avg cor}
cor(evals$score,evals$bty_avg)
```

Sure enough. The correlation is very small. 

### Exercise 3

```{r geom_jitter}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() 
```

Jitter here is adding a little bit of random variation to the location of each point. This helps in that the initial plot isn't doing this because the score variable is a discrete variable. What's misleading about the initial plot is that it assumes that there is no random variation when someone gives one particular score. Just because someone may give a score of 4 doesn't mean that their following the same criteria as someone else also giving that 4. Everyone gives that 4 for slightly different reasons. Jitter helps to communicate this. 

```{r}

```

