---
title: "Lab 09"
author: "Conor Lacey"
date: '2023-03-17'
output: github_document
---

### Libraries

```{r Libraries}
library(tidyverse) 
library(broom)
library(openintro)
library(skimr)
```

### Exercise 1

```{r Score}
evals %>% ggplot(aes(x = score)) +
  geom_density(fill = "blue", alpha = 0.5)

summary(evals$score)
```

In general students rate courses pretty high. However, there it is skewed to the left. I would expect this as much, given that most students will do well in a class, getting a B or above and hence will give the professor a good rating. However, a few students will do exteremly poor in the class and hence blame some of their poor behavior on the professor. 

### Exercise 2

```{r score & bty_avg}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_point() + 
  geom_smooth()
```

In general, the relationship between score and beauty average appears to be random. 


```{r score & bty_avg cor}
cor(evals$score,evals$bty_avg)
```

Sure enough. The correlation is very small. 
