---
title: "Lab 09"
author: "Conor Lacey"
date: '2023-03-17'
output: github_document
---

### Libraries

```{r Libraries}
suppressWarnings(library(tidyverse))
suppressWarnings(library(broom))
suppressWarnings(library(openintro))
```

### Exercise 1

```{r Score}
evals %>% ggplot(aes(x = score)) +
  geom_density(fill = "blue", alpha = 0.5)

summary(evals$score)
```

In general students rate courses pretty high. However, there it is skewed to the left. I would expect this as much, given that most students will do well in a class, getting a B or above and hence will give the professor a good rating. However, a few students will do exteremly poor in the class and hence blame some of their poor behavior on the professor. 

### Exercise 2

```{r score & bty_avg}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_point() 
```

In general, the relationship between score and beauty average appears to be random. 


```{r score & bty_avg cor}
cor(evals$score,evals$bty_avg)
```

Sure enough. The correlation is very small. 

### Exercise 3

```{r geom_jitter}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() 
```

Jitter here is adding a little bit of random variation to the location of each point. This helps in that the initial plot isn't doing this because the score variable is a discrete variable. What's misleading about the initial plot is that it assumes that there is no random variation when someone gives one particular score. Just because someone may give a score of 4 doesn't mean that their following the same criteria as someone else also giving that 4. Everyone gives that 4 for slightly different reasons. Jitter helps to communicate this. 

### Exercise 4

```{r m_bty}
m_bty <- lm(evals$score ~ evals$bty_avg)
summary(m_bty)
```

Linear model is: 

score = 3.88 + .067*bty_avg.

### Exercise 5

```{r evals plot with lm}
evals %>% ggplot(aes(x = score, y = bty_avg)) + 
  geom_jitter() + 
  stat_smooth(method = lm, se = FALSE, color = "orange")
```

### Exercise 6

Given the linear model, there is a positive relationship between score and beauty average such that as score increases so does beauty average. 

### Exercise 7

The intercept is 3.88 which means that with a score of 0 the mean average beauty rating is 3.88. I guess this would make sense. This is a relatively low score and I assume that those who do not do well in a class may hold animosity towards their professors such that they give them low beauty ratings. 

### Exercise 8 

The R^2 value is 0.035 meaning 3.5% of the variance in average beauty ratings can be explained by a professor's average evaluation score.

### Exercise 9

```{r score by gender lm}
m_gen <- lm(evals$score ~ evals$gender)
summary(m_gen)
```

The linear model is: 

score = .14*gender + 4.09 


The intercept indicates that female professors earn an average evaluation score of 4.09. The slope indicates that if a professor is male the average evaluation score is .14 more than the female average evaluation score. 


### Exercise 10 

Equation for females:

score = 4.09

Equation for males:

score = 4.23

### Exercise 11

```{r score by rank lm}
m_rank <- lm(evals$score ~ evals$rank)
summary(m_rank)
```

The regression model is: 

score = 4.28 + tenture_track*-.13 + tenured*-.16


The intercept indicates that the mean average teaching professor score is 4.28. The slope of tenure_track indicates that that mean average tenture track professor score is 4.28-.13, or 4.15. Lastly, the slope of tentured indicates that the mean average tenured professor score is 4.28 - .16, or 4.12. 

### Exercise 12 

```{r rank_relevel}
evals <- evals %>% mutate(rank_relevel = case_when(rank == "tenure track" ~ 0,
                                          rank == "teaching" ~ 1,
                                          rank == "tenured" ~ 2))
```

### Exercise 13

```{r score by rank_relevel lm}
m_rank_relevel <- lm(evals$score ~ evals$rank_relevel)
summary(m_rank_relevel)
```

The linear model is: 

score = 4.2 + rank_relevel*-0.02


In this linear model the intercept indicates that the mean average tenure track professor score is 4.2. The slope of rank_level indicates that mean average teaching professor score is 4 and the mean average tenured professor score is 3.98. 

The R^2 value is 0.001 meaning the the rank_relevel variable explains 0.1% of the of the variance in average professor evaluation scores. 

### Exercise 14

```{r tenure_eligible}
evals <- evals %>% mutate(tenure_eligible = if_else(rank == "tenure track" | rank == "tenured", 
                                                    "yes", "no"))
```

### Exercise 15

